Computational biology in the 21st century: Algorithms that scale

### 2015-07-28 main.tex
ACM fails single-point-of-truth for titles.
Mass spectroscopy ==> mass spectrometry
Spectroscopy is an old and now discouraged term, though correct.

\acmformat{Bonnie Berger, Noah M. Daniels,
and Y. William Yu, 2015. Title.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

Computational biologists answer biological and biomedical 
questions by using computation in support of---or in place of---laboratory 
procedures, in hopes of obtaining more accurate answers at a greatly reduced 
cost.
The past two decades have seen unprecedented technological progress with regard
to generating biological data; next-generation sequencing, mass spectroscopy,
microarrays, nuclear magnetic resonance spectroscopy, and other high-throughput 
approaches have led to an explosion of data.
However, this explosion of data is a mixed blessing.
On the one hand, the scale and scope of data should allow new insights into
genetic and infectious diseases, cancer, basic biology, and even human migration
patterns.
On the other hand, researchers are generating datasets so massive that it has 
become difficult to analyze them to discover patterns that give clues to the 
underlying biological processes.

>>>>

\acmformat{Bonnie Berger, Noah M. Daniels,
and Y. William Yu, 2015. Computational biology in the 21st century: Algorithms that scale.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

Computational biologists answer biological and biomedical 
questions by using computation in support of---or in place of---laboratory 
procedures, in hopes of obtaining more accurate answers at a greatly reduced 
cost.
The past two decades have seen unprecedented technological progress with regard
to generating biological data; next-generation sequencing, mass spectrometry,
microarrays, nuclear magnetic resonance spectroscopy, and other high-throughput 
approaches have led to an explosion of data.
However, this explosion of data is a mixed blessing.
On the one hand, the scale and scope of data should allow new insights into
genetic and infectious diseases, cancer, basic biology, and even human migration
patterns.
On the other hand, researchers are generating datasets so massive that it has 
become difficult to analyze them to discover patterns that give clues to the 
underlying biological processes.
